Efficient Calculation of Regularized Discriminant Analysis for High-Dimensional Classification

### 2013-12-11 reports/paper-hdrda.Rnw
Updated paper's title.

\title{High-Dimensional Regularized Discriminant Analysis}

@@

The smallest eigenvalues and the directions associated with their eigenvectors
highly influence \eqref{eq:qda}. In fact, the eigenvalues of $\widehat{ \bm
  \Sigma}_k$ are well-known to be biased if $p \ge n_k$ such that the smallest
eigenvalues are underestimated \citep{Seber:2004uh}, Moreover, if $p > n_k$,
then rank$(\widehat{\bm \Sigma}_k) \le n_k$, which implies that at least $p -
n_k$ eigenvalues of $\widehat{\bm \Sigma}_k$ are zero. Furthermore, although
more feature information is available to discriminate among the $K$ classes, if
$p > n_k$, \eqref{eq:qda} is incalculable because $\widehat{\bm \Sigma}_k^{-1}$
does not exist.

>>>>

\title{Efficient Calculation of Regularized Discriminant Analysis for
  High-Dimensional Classification}

@@

The smallest eigenvalues and the directions associated with their eigenvectors
highly influence \eqref{eq:qda}. In fact, the eigenvalues of $\widehat{ \bm
  \Sigma}_k$ are well-known to be biased if $p \ge n_k$ such that the smallest
eigenvalues are underestimated \citep{Seber:2004uh}. Moreover, if $p > n_k$,
then rank$(\widehat{\bm \Sigma}_k) \le n_k$, which implies that at least $p -
n_k$ eigenvalues of $\widehat{\bm \Sigma}_k$ are zero. Furthermore, although
more feature information is available to discriminate among the $K$ classes, if
$p > n_k$, \eqref{eq:qda} is incalculable because $\widehat{\bm \Sigma}_k^{-1}$
does not exist.
